District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-10 paper/paper.tex
Add plots to TeX file

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

@@

\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \caption{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}
\end{figure}

@@

\emph{Figure 2: Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries.} 
\emph{Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana.}

TODO: Remove superfluous whitespace here!

@@

\emph{Figure 3: District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.}
\emph{Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).}
\emph{Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}

@@

\emph{Figure 4: Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020. The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy. Purple areas represent countries where circumcision type could not be ascertained from surveys.}

@@

\subsection{Decrease in TMC in SSA region Over Time}
\label{sec:org5fb5e18}
\emph{Figure 6: Number of men aged 10-29 years who were medically circumcised and traditionally circumcised each year between 2010 and 2020. The lighter shaded area represents projection after the most recent household survey. Purple areas represent countries where circumcision type could not be ascertained from surveys.}

>>>>

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\usepackage{todonotes}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

@@

% Surveys Plot (may be moved to supp. figs)
\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \includegraphics[width=.9\linewidth]
    {plots/01_survey_table.png}
    \caption{\emph{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}}
\end{figure}

@@

% Map Plot
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/02_map_plot_facet.png}
    \caption{\emph{Estimated percentage of men aged 10-29 years who were circumcised subnationally in 33 SSA countries in 2006 and 2020, as well as the difference in coverage between the two years. Maps show total male circumcision (MC), medical male circumcision (MMC) and traditional male circumcision (TMC), for which the negative change from 2006 to 2020 is shown, respectively. Missing from map: Guinea-Bissau, Equitorial Guinea, Central African Republic and Botswana}}
\end{figure}

@@

% Subnational coverage plot
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/03_subnat_plot.png}
    \caption{\emph{District-level median percentage of men aged 10-29 years who were circumcised in 2020 in 33 SSA countries.
    Each point is a district, sized by district population relative to average district size and coloured by the African region their country falls under (Eastern and Southern Africa (ESA) and Western and Central Africa (WCA), respectively).
    Each white dot represents the national median. A vertical dotted line signifies the UNAIDS target of 90\% national MC.}}
\end{figure}

@@

% Geofaceted plot of 2020 coverage by age
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/04_geo_age.png}
    \caption{\emph{Projected percentage of men from 0 to 60 years old who were medically circumcised and traditionally circumcised by 2020. The horizontal grey dashed line indicates the 90\% circumcision coverage by 2021 target established by the UNAIDS Fast Track strategy. Purple areas represent countries where circumcision type could not be ascertained from surveys.}}
\end{figure}

@@

\subsection{Decrease in TMC in SSA region Over Time}
\label{sec:org5fb5e18}

% Dumbbell of type-specific cov change 00'-20'
% todo: Rewrite caption
\begin{figure}
    \centering
    \includegraphics[width=.9\linewidth]
    {plots/05_change_00_20.png}
    \caption{\emph{Absolute difference, with associated errors, in percentage coverage from 2000 to 2020, coloured by sub-Saharan African region. Plots are split by circumcision type. Countries are ordered from north to south, east to west, and the 13 countries below the black horizontal lines are VMMC priority countries.  }}
\end{figure}
